A Meta-analysis of Longevity Estimates of Mosquito Vectors of Disease: Supplementary Figures

### 2018-12-05 supplementary_materials.tex
Changed comparison figures to account for the two extra species that overlap
Made changes to the results MS as per Ace's comments

\begin{table}[htbp]
	\centering
	\begin{tabular}{l|l|l|l|l}
		species & \multicolumn{1}{l}{$\text{df}_1$} & \multicolumn{1}{l}{$\text{df}_2$} & \multicolumn{1}{l}{F} & \multicolumn{1}{l}{p} \\
		\midrule
		\textit{Ae. aegypti} & 1     & 55    & 2.2   & 0.14 \\
		\textit{A. darlingi} & 1     & 6     & 114.8   & 0.00 \\
		\textit{An. farauti s.l.} & 1     & 14    & 0.9  & 0.35 \\
		\textit{A. gambiae s.l.} & 1     & 37    & 3.9   & 0.06 \\
		\textit{Cx. pipiens} & 1     & 13    & 0.6   & 0.47 \\
		\textit{A. quadrimaculatus} & 1     & 8     & 2.4     & 0.16 \\
		\textit{Cx. quinquefasciatus} & 1     & 13    & 2.2    & 0.17 \\
		\textit{A. sergentii} & 1     & 8     & 0.4     & 0.55 \\
		\textit{Cx. tritaeniorhynchus} & 1     & 5     & 3.5   & 0.12 \\
		\textit{Ae. vexans} & 1     & 2     & 1.2   & 0.39 \\
	\end{tabular}%
	\caption{\textbf{The results of comparisons between LBLs for those species with data for MRRs and dissection-based studies.} The ANOVA tests were conducted using median posterior LBLs estimated at the time-series level.}
	\label{tab:comparison}%
\end{table}%

@@

>>>>

\begin{table}[htbp]
	\centering
	\begin{tabular}{l|l|l|l|l}
		species & \multicolumn{1}{l}{$\text{df}_1$} & \multicolumn{1}{l}{$\text{df}_2$} & \multicolumn{1}{l}{F} & \multicolumn{1}{l}{p} \\
		\midrule
		\textit{Ae. aegypti} & 1     & 55    & 1.9   & 0.17 \\
		\textit{A. culicifacies s.l.} & 1     & 19    & 2.2   & 0.15 \\
		\textit{A. darlingi} & 1     & 6     & 80.7   & 0.00 \\
		\textit{An. farauti s.l.} & 1     & 14    & 2.1  & 0.17 \\
		\textit{A. gambiae s.l.} & 1     & 37    & 4.3   & 0.05 \\
		\textit{Cx. pipiens} & 1     & 13    & 0.4   & 0.56 \\
		\textit{A. quadrimaculatus} & 1     & 8     & 2.2     & 0.18 \\
		\textit{Cx. quinquefasciatus} & 1     & 13    & 2.2    & 0.16 \\
		\textit{A. sergentii} & 1     & 8     & 1.0    & 0.36 \\
		\textit{A. subpictus} & 1     & 2    & 11.4   & 0.08 \\
		\textit{Cx. tritaeniorhynchus} & 1     & 5     & 3.6   & 0.12 \\
		\textit{Ae. vexans} & 1     & 2     & 1.1   & 0.41 \\
	\end{tabular}%
	\caption{\textbf{The results of comparisons between LBLs for those species with data for MRRs and dissection-based studies.} The ANOVA tests were conducted using median posterior LBLs estimated at the time-series level.}
	\label{tab:comparison}%
\end{table}%

@@

\begin{figure}[ht]
	\centerline{\includegraphics[width=1\textwidth]{./Figure_files/elpd_comparison.pdf}}
	\caption{\textbf{Comparing the evidence for age-dependent mortality by fitting the Gompertz model to data from the MRR versus dissection studies for the 12 species with data from both.} The points indicate the estimated predictive accuracy compared with the exponential model (see SOM Methods) and the lower and upper whiskers represent 2.5\% and 97.5\% quantiles on this quantity.}\label{fig:elpd_comparison}
\end{figure}
